### 2024-03-22 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - updated

::: {.sourceClojure}
```clojure
(delay
  (-> processed-trips
      (tc/add-column :cluster (:clustering clustering))
      (tc/group-by [:cluster])
      (tc/without-grouping->
       (tc/order-by (fn [ds]
                      (-> ds :data tc/row-count))
                    :desc)
       (tc/head 5))
      (tc/aggregate {:n tc/row-count
                     :hours (fn [trips]
                              [(hour-counts-plot trips)])
                     :map (fn [trips]
                            [(-> trips
                                 (tc/random 1000 {:seed 1})
                                 (hanami/plot ht/layer-chart
                                              {:TITLE "Chicago bike trips"
                                               :LAYER [{:data {:url "notebooks/chicago.geojson"
                                                               :format {:type "topojson"}}
                                                        :mark {:type "geoshape"
                                                               :filled false
                                                               :clip true
                                                               :opacity 0.3}}
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/rule-chart
                                                                     {:X :start_lat
                                                                      :Y :start_lng
                                                                      :X2 :end_lat
                                                                      :Y2 :end_lng
                                                                      :OPACITY 0.01}))
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/point-chart
                                                                     {:X :start_lat
                                                                      :Y :start_lng
                                                                      :MCOLOR "purple"
                                                                      :OPACITY 0.01}))
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/point-chart
                                                                     {:X :end_lat
                                                                      :Y :end_lng
                                                                      :MCOLOR "green"
                                                                      :OPACITY 0.01}))]}))])})
      kind/table))
```
:::

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>15</td><td>13103</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>11728</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11427</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>56</td><td>11393</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>36</td><td>11366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

>>>>

::: {.sourceClojure}
```clojure
(delay
  (-> processed-trips
      (tc/add-column :cluster (:clustering clustering))
      (tc/group-by [:cluster])
      (tc/without-grouping->
       (tc/order-by (fn [ds]
                      (-> ds :data tc/row-count))
                    :desc)
       (tc/head 5))
      (tc/aggregate {:n tc/row-count
                     :hours (fn [trips]
                              [(hour-counts-plot trips)])
                     :map (fn [trips]
                            [(-> trips
                                 (hanami/plot ht/layer-chart
                                              {:TITLE "Chicago bike trips"
                                               :LAYER [{:data {:url "notebooks/chicago.geojson"
                                                               :format {:type "topojson"}}
                                                        :mark {:type "geoshape"
                                                               :filled false
                                                               :clip true
                                                               :opacity 0.3}}
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/rule-chart
                                                                     {:X :start_lat
                                                                      :Y :start_lng
                                                                      :X2 :end_lat
                                                                      :Y2 :end_lng
                                                                      :OPACITY 0.01}))
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/point-chart
                                                                     {:X :start_lat
                                                                      :Y :start_lng
                                                                      :MCOLOR "purple"
                                                                      :OPACITY 0.01}))
                                                       (as-geo
                                                        (hanami/plot nil
                                                                     ht/point-chart
                                                                     {:X :end_lat
                                                                      :Y :end_lng
                                                                      :MCOLOR "green"
                                                                      :OPACITY 0.01}))]}))])})
      kind/table))
```
:::

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>57</td><td>13013</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>12917</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>7</td><td>12853</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>12666</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>11639</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
